---
title: "Untitled"
output:
  github_document:
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '') # do not show NA in tables
```

```{r, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
library(here)
library(readr)
library(dplyr)
library(knitr)
library(kableExtra)

tbl_doc <- readr::read_tsv(here::here('./docs/oss2_table_documentation.tsv'))
```
# OSS2

The code for pulling the data used in the OSS project/paper to measure the cost of open-source software by looking at lines of code

###### Comments about this README document
**DO NOT** edit the `README.md` file directly, it is generated from the `./docs/README/README.Rmd` file by running

```bash
make readme
```

If you use a version of R < 3.5 (i.e., 3.4), you will see the back slash `\` before the underscores `_` in the rendered tables.
Please see this related issue: https://github.com/haozhu233/kableExtra/issues/186


# CRAN Logs

Script that downloaded the daily package download logs and daily r-base download logs from the rstudio CRAN mirror:
`./analysis/01-scrape_package_data/cran/logs`

- package: `'./data/oss2/original/cran/logs/pkg/'`
- r-base: `'./data/oss2/original/cran/logs/r/'`

# Lines of Code Analysis

In general, the scripts under `Getting Data` are making API calls,
and running them may take a long time (or may not work depending on API changes).

### R (CRAN)

### Python (PyPI)

Running order

1. Getting Data: `./analysis/01-scrape_package_data/pypi/`
2. Processing Data: `./analysis/02-process_scraped/pypi/`

```{r}
tbl_doc %>%
  dplyr::select(run_order, "Getting Data":Notes) %>%
  knitr::kable() %>%
  kableExtra::kable_styling(full_width = TRUE)
```

```{r}
tbl_doc %>%
  dplyr::select(run_order, "Getting Data":"Github", input:output) %>%
  knitr::kable() %>%
  kableExtra::kable_styling(full_width = TRUE)
```



### JavaScript (CDN)

Running order

| Getting Data               	| Parsing Data                            	|
|----------------------------	|-----------------------------------------	|
| 01-get_pkg_json_info.R     	|                                         	|
|                            	| 01-cdn_pkg_info.R                       	|

1. `01-get_pkg_json_info.R`: download package infor from `https://api.cdnjs.com/libraries/`
  - input: None
  - output: `/data/oss2/original/cdn/libraries_json/`

  - input: `'./data/oss2/original/cdn/libraries_json/'`

### Julia
