---
title: "OSS2"
output:
  github_document:
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '') # do not show NA in tables
```

```{r, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
library(here)
library(readr)
library(dplyr)
library(knitr)
library(kableExtra)

show_notes <- function(df) {
  df %>%
    dplyr::select(run_order, "Getting Data":Notes) %>%
    knitr::kable() %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                              full_width = TRUE)
}

show_io <- function(df) {
  df %>%
    dplyr::select(run_order, "Getting Data":"Github", input:output) %>%
    knitr::kable() %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                              full_width = TRUE)
}

tbl_doc <- readr::read_tsv(here::here('./docs/oss2_table_documentation.tsv'))
```

The code for pulling the data used in the OSS project/paper to measure the cost of open-source software by looking at lines of code

###### Comments about this README document
**DO NOT** edit the `README.md` file directly, it is generated from the `./docs/README/README.Rmd` file by running

```bash
make readme
```

If you use a version of R < 3.5 (i.e., 3.4), you will see the back slash `\` before the underscores `_` in the rendered `html` tables.
Please see this related issue: https://github.com/haozhu233/kableExtra/issues/186.
However you'll still see the `\` before the underscores in the final markdown output (see issue: )


# CRAN Logs

Script that downloaded the daily package download logs and daily r-base download logs from the rstudio CRAN mirror:
`./analysis/01-scrape_package_data/cran/logs`

This script dumps out the r and package logs in the following folders:

- package: `'./data/oss2/original/cran/logs/pkg/'`
- r-base: `'./data/oss2/original/cran/logs/r/'`

# Lines of Code Analysis

In general, the scripts under `Getting Data` are making API calls,
and running them may take a long time (or may not work depending on API changes).
Code that parses downloaded data are in the `Processing Data` section.
Github `clones` are under the `Github` section.

### Package Counts

Data for the table and figures come from `./docs/package_counts/package_counts.Rmd`.
**DO NOT** edit the `.dot` file in `./docs/package_counts/package_count.dot`, it is generated from the `.Rmd` document.

If these numbers are not updating after making changes to `package_counts.Rmd`, try running:

```bash
make package_counts
```

```{r, echo=FALSE, message=FALSE}
all_cts <- readr::read_csv(here::here('./docs/package_counts/package_counts.csv'))

knitr::kable(all_cts) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                            full_width = TRUE)
```

```{r, echo=FALSE}
library(DiagrammeR)

DiagrammeR::grViz(diagram = here::here('./docs/package_counts/package_count.dot'))
```

### R (CRAN)

```{r}
cran <- tbl_doc %>%
  dplyr::filter(analysis == 'cran')
```


Running order

1. Getting Data: `./analysis/01-scrape_package_data/cran/cran_data/`
2. Processing Data: `./analysis/02-process_scraped/cran/`
3. Github: `./analysis/03-github/`

```{r, results='asis'}
show_notes(cran)
```

```{r, results='asis'}
show_io(cran)
```


### Python (PyPI)

```{r}
pypi <- tbl_doc %>%
  dplyr::filter(analysis == 'pypi')
```


Running order

1. Getting Data: `./analysis/01-scrape_package_data/pypi/`
2. Processing Data: `./analysis/02-process_scraped/pypi/`
3. Github: `./analysis/03-github/`

```{r, results='asis'}
show_notes(pypi)
```

```{r, results='asis'}
show_io(pypi)
```

### JavaScript (CDN)

```{r}
cdn <- tbl_doc %>%
  dplyr::filter(analysis == 'cdn')
```

```{r}
show_notes(cdn)
```

```{r}
show_io(cdn)
```



### Julia

```{r}
julia <- tbl_doc %>%
  dplyr::filter(analysis == 'julia')
```

```{r}
show_notes(julia)
```

```{r}
show_io(julia)
```

