---
title: "package_counts"
output: 
  html_document: 
    keep_md: yes
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r, warning=FALSE, results=FALSE, message=FALSE}
library(here)
library(readr)
library(dplyr)
library(rvest)
library(tibble)

knitr::opts_chunk$set(message = FALSE)
```


# CRAN

### Total

Total number of cran packages

```{r}
cran_pkgs <- readr::read_csv(here::here('./data/oss2/processed/pkg_links.csv'))
```

Total number of cran packages

```{r}
TOTAL_CRAN <- nrow(cran_pkgs)
stopifnot(TOTAL_CRAN == length(unique(cran_pkgs$pkg_name)))
TOTAL_CRAN
```

### Production

Total number of production ready packages

```{r}
cran_production_status <- readr::read_csv(here::here('./data/oss2/processed/cran/cran_prod_rdy.csv'))

table(cran_production_status$production_ready, useNA = 'always')
```

```{r}
PRODUCTION_CRAN <- cran_production_status %>% dplyr::filter(production_ready == TRUE) %>% nrow()
PRODUCTION_CRAN
```

### OSI

Total number of OSI packages

```{r}
cran_osi_status <- readr::read_rds(here::here('./data/oss2/processed/cran/cran_osi_licenses.RDS'))
table(cran_osi_status$osi_approved, useNA = 'always')
```

```{r}
OSI_CRAN <- cran_osi_status %>% dplyr::filter(osi_approved == TRUE) %>% nrow()
OSI_CRAN
```

Production ready packages with OSI approved licenses

```{r}
prod <- readr::read_csv(here::here('./data/oss2/processed/cran/cran_prod_rdy.csv'))
osi <- readr::read_rds(here::here('./data/oss2/processed/cran/cran_osi_licenses.RDS'))
stopifnot(nrow(osi) == nrow(prod))
prod_osi <- dplyr::full_join(prod, osi, by = c('pkg_name', 'pkg_description', 'pkg_links', 'pkg_path'))
stopifnot(nrow(prod_osi) == nrow(prod))
```

```{r}
addmargins(table(prod_osi$production_ready, prod_osi$osi_approved, useNA = 'always'))
```

### Prod + OSI

```{r}
cran_production_osi_status <- readr::read_rds(here::here(
  './data/oss2/processed/cran/production_ready_osi_approved.RDS'))

PRODUCTION_OSI_CRAN <- nrow(cran_production_osi_status)
PRODUCTION_OSI_CRAN
```

### Prod + OSI + GH

Production ready, OSI approved packages with a github slug

```{r}
github_cran <- readr::read_rds(here::here('./data/oss2/processed/cran/production_osi_gh.RDS'))
```

```{r}
table(!is.na(github_cran$gh_slug), useNA = 'always') %>% addmargins()
```


```{r}
PROD_OSI_GH_CRAN <- github_cran %>% dplyr::filter(!is.na(gh_slug)) %>% nrow()
```

### GH Cloned

Production ready, OSI approved packages with a github slug that were cloned

```{r}
cloned <- list.dirs(here::here('./data/oss2/original/cloned_repos/cran'),
                    full.names = TRUE, recursive = FALSE)

CLONED_CRAN <- length(cloned)
CLONED_CRAN
```


# Python

### Total

```{r}
pypi_pkgs <- xml2::read_html(here::here(
  './data/oss2/original/pypi/pypi_simple/2019-01-23-pypi_simple.html'))

pkg_urls <- pypi_pkgs %>%
  rvest::html_nodes('a') %>%
  rvest::html_attr('href')
```

```{r}
TOTAL_PYPI <- length(pkg_urls)
TOTAL_PYPI
```

### Production


```{r, warning=FALSE}
prod_mature_packages <- readr::read_csv(here::here(
  './data/oss2/processed/working/pypi/production_ready.csv'))

prod_mature_packages$dev_status_clean %>% table(useNA = 'always') %>% addmargins()
```

```{r}
PRODUCTION_PYPI <- prod_mature_packages %>%
  dplyr::filter(dev_status_clean %in% c('production/stable', 'mature')) %>%
  nrow()
PRODUCTION_PYPI
```

### OSI

```{r}
osi_pypi <- readr::read_rds(here::here('./data/oss2/processed/pypi/osi_approved.RDS'))

table(osi_pypi$osi_approved, useNA = 'always') %>% addmargins()
```

```{r}
OSI_PYPI <- osi_pypi %>%
  dplyr::filter(osi_approved == TRUE) %>%
  nrow()
```

### Prod + OSI

Production ready and OSI

```{r, warning=FALSE}
prod_rdy <- readr::read_csv(here::here('./data/oss2/processed/working/pypi/production_ready.csv'))
prod_rdy <- dplyr::mutate(prod_rdy, prod_rdy = dev_status_clean == 'production/stable' | dev_status_clean == 'mature')

osi_appr <- readr::read_rds(here::here('./data/oss2/processed/pypi/osi_approved.RDS'))
prod_osi_status <- dplyr::full_join(prod_rdy, osi_appr, by = c('name'))
```

`prod_osi_status$prod_rdy` as rows; `prod_osi_status$osi_approved` are columns
```{r}
table(prod_osi_status$prod_rdy, prod_osi_status$osi_approved, useNA = 'always') %>% addmargins()
```


```{r}
PRODUCTION_OSI_PYPI <- dplyr::filter(prod_osi_status,
                          prod_rdy == TRUE,
                          osi_approved == TRUE) %>%
  nrow()
PRODUCTION_OSI_PYPI
```

### Prod + OSI + GH


```{r}
prod_osi_gh_pypi <- readr::read_rds(here::here('./data/oss2/processed/pypi/prod_osi_gh.RDS'))
```

```{r}
PROD_OSI_GH_PYPI <- nrow(prod_osi_gh_pypi)
```

### GH Cloned

Production ready with OSI approved licenses that were downloaded for analysis in github.

```{r}
CLONED_PYPI <- dir.exists(here::here(prod_osi_gh_pypi$gh_clone_path)) %>% sum(na.rm = TRUE)
CLONED_PYPI
```


# Complete Table Count

```{r}
all_cts <- tibble::tribble(
  ~Variable,              ~CRAN,               ~PyPI,               ~Julia, ~CDN,
  "Total",                TOTAL_CRAN,          TOTAL_PYPI,          NA,     NA,
  "Production Ready",     PRODUCTION_CRAN,     PRODUCTION_PYPI,     NA,     NA,
  "OSI Approved License", OSI_CRAN,            OSI_PYPI,            NA,     NA, 
  "Prod + OSI",           PRODUCTION_OSI_CRAN, PRODUCTION_OSI_PYPI, NA,     NA, 
  "Prod + OSI + Github",  PROD_OSI_GH_CRAN,    PROD_OSI_GH_PYPI,    NA,     NA,
  "Cloned",               CLONED_CRAN,         CLONED_PYPI,         NA,     NA
) %>%
  dplyr::mutate(cran_pypi = CRAN + PyPI)
knitr::kable(all_cts)
```

# Consort Diagram

```{r}
library(DiagrammeR)
library(glue)
```

```{r}
glue::glue('hello \\{')
```


```{r, echo=FALSE}
dot_f <- glue('
digraph g {
  cran000 [shape = box, label = "CRAN\n<<TOTAL_CRAN>>"];
  cran010 [shape = box, label = "Production ready\nN=<<PRODUCTION_CRAN>>"];
  cran020 [shape = box, label = "OSI\nN=<<OSI_CRAN>>"];
  cran025 [shape = box, label = "Production + OSI\nN=<<PRODUCTION_OSI_CRAN>>"];
  cran030 [shape = box, label = "Production + OSI + Github\nN=<<PROD_OSI_GH_CRAN>>"];
  cran035 [shape = box, label = "Production + OSI + Github + Clone\nN=<<CLONED_CRAN>>"];

  py000 [shape = box, label = "PyPI\nN=<<TOTAL_PYPI>>"];
  py010 [shape = box, label = "Production/Stable/Mature\nN=<<PRODUCTION_PYPI>>"];
  py020 [shape = box, label = "OSI\nN=<<OSI_PYPI>>"];
  py025 [shape = box, label = "Production + OSI\nN=<<PRODUCTION_OSI_PYPI>>"];
  py030 [shape = box, label = "Production + OSI + Github\nN=<<PROD_OSI_GH_PYPI>>"];
  py040 [shape = box, label = "Production + OSI + Github + Clone\nN=<<CLONED_PYPI>>"];

  cran000 -> cran010;
  cran000 -> cran020;
  cran010 -> cran025;
  cran025 -> cran030;
  cran030 -> cran035;

  py000 -> py010;
  py000 -> py020
  py010 -> py025;
  py025 -> py030;
  py030 -> py040;
}', .open = "<<", .close = ">>")
```

```{r}
grViz(diagram = dot_f)
```

